---
title: "lab6andrews"
author: "Christopher Andrews"
date: "11/26/2018"
output: word_document
---

```{r setup, include=FALSE, cache=TRUE}
knitr::opts_chunk$set(echo = TRUE)
set.seed(787)
```

```{r}
download.file("http://www.openintro.org/stat/data/ames.RData", destfile =
"ames.RData")
load("ames.RData")
```

```{r}
population <- ames$Gr.Liv.Area
samp <- sample(population, 60)
```

➡ Exercise 1: Plot a histogram of your sample of living areas. Then, describe the shape,
center, and spread of your histogram. What would you say is the “typical” living area within
your sample? Explain.

The center is around 1607...
The shape of the main part of the histogram is symmetrical...
There looks to be at least one outlier around 3400...
I would say the typical living area based on the sample is 1632..
```{r}
hist(samp,breaks = 25)
summary(samp)
sd(samp)
```

➡ Exercise 2: Would you expect another student’s sample distribution to be identical to
yours? Would you expect it to be similar? Why or why not?

No, I would not expect another student's sample distribution to be identical. I would
expect it to be entirely different. But, there is defintely a small chance that
the sampling distribution would be exactly the same.
I would expect the sampling another student's sample distribution to be somewhat similar.

```{r}
sample_mean <- mean(samp)
```

```{r}
se <- sd(samp)/sqrt(60)
lower <- sample_mean - 2 * se
upper <- sample_mean + 2 * se
c(lower, upper)
```

➡ Exercise 3: For a one-sample t confidence interval to be valid, the sampling distribution of
the sample mean must be normally distributed. Check this assumption using the indirect
methods demonstrated during class. (Note: If any outliers are present in your sample, you will
need to include the relevant calculations to classify the outlier(s) as being either mild or extreme.
Extreme outliers prevent us from applying the Central Limit Theorem.) 



```{r}
boxplot(samp)
shapiro.test(samp)
qqnorm(samp)
qqline(samp)
```

➡ Exercise 4: Report your 95% confidence interval in the form . Then,
carefully interpret your confidence interval in context.

